Stuff that may well go into the project report

### 2014-09-29 stuff_somewhat_organised.tex
Getting OK along with Ladyzhenskaya.

\setcounter{obs}{0}
\begin{obs}
Provided $\iint_{Q_T} f\Phi(u)dxdt$ in (\ref{energy_ineq}) makes sense, $\Phi(u) \in L^2(0,T: H_0^1(\Omega))$ for weak energy solutions. If we can put on a condition on $u$ or any of the data to ensure that $u \in L^2(Q_T)$, we would have a condition under which weak energy solutions are unique. Hopefully, no such condition is required, but will perhaps follow from some other estimate.
\end{obs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%				APPENDICES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{appendices}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		A
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Passing derivative inside the integral}
\label{sec:derivative}

@@

To get the more general (\ref{diff_int}), we simply apply this result for each individual spatial dimension while keeping the others fixed.

%%%%%%%%%%%%%%%%%%
%		B
%%%%%%%%%%%%%%%%%%
\section{Some major theorems}
We now consider the problem of determining a function $u = u(x,t)$ in $\overline{Q}_T$ so that
\begin{equation}
\label{lady_parabolic_eq}
	u_t - \sum_{i=1}^d\frac{d}{dx_i}a_i(x,t,u,\nabla u) + a(x,t,u,\nabla u) = 0
\end{equation}
in $Q_T$ and on $\Gamma_T$
\begin{equation}
\label{lady_bc}
	u\big|_{\Gamma_T} = \psi\big|_{\Gamma_T}
\end{equation}
for some known function $\psi$.

@@

	\item For $(x,t) \in \overline{Q}_T$, $|u| \leq M$ and arbitrary $p$ the functions $a_i(x,t,u,p)$ and $a(x,t,u,p)$ are continuous, the $a_i(x,t,u,p)$ are differentiable with respect to $x$, $u$ and $p$ and the following inequalities are satisfied
	\begin{equation}
	\label{exist_cond3}
		\begin{cases}
			\nu\xi^2 \leq \frac{\partial a_i(x,t,u,p)}{\partial p_j}\xi_i \xi_j \leq \mu \xi^2, \quad \nu > 0 \\
			\sum_{i=1}^d \left(|a_i| + |\frac{\partial a_i}{\partial u}|\right)(1+|p|) + \sum_{i,j=1}^d |\frac{\partial a_i}{\partial x_j}| + |a| \leq \mu (1 + |p|)^2. 		
		\end{cases}
	\end{equation}
	where $\nu$ and $\mu$ are positive numbers.

	\item For $(x,t) \in \overline{Q}_T$, $|u| \leq M$ and $|p| \leq M_1$, the functions $a_i$, $a$, $\frac{\partial a_i}{\partial p_j}$, $\frac{\partial a_i}{\partial u}$, and $\frac{\partial a_i}{\partial x_i}$ are continuous functions satisfying a H\H{o}lder condition in $x$, $t$, $u$ and $p$ with exponents $\beta$, $\frac{\beta}{2}$, $\beta$ and $\beta$ respectively.

@@

\subsection{This existence result applied to our problem}
The general porous medium equation we are concerned with can be written
\begin{equation*}
u_t - \nabla \cdot (\nabla \Phi(u) ) - f(x,t) = 0,
\end{equation*}
which is of the form (\ref{lady_parabolic_eq}) with
\begin{equation}
a_i(x,t,u,\nabla u) = \Phi'(u) u_{x_i}, \quad a(x,t,u,\nabla) = -f(x,t).
\end{equation}

@@

	In the general porous medium equation
	\begin{equation*}
		A(x,t,u,p) = -f(x,t) - 
	\end{equation*}
\end{enumerate}
\end{appendices}

>>>>

\setcounter{obs}{0}
\begin{obs}
Provided $\iint_{Q_T} f\Phi(u)dxdt$ in (\ref{energy_ineq}) makes sense, $\Phi(u) \in L^2(0,T: H_0^1(\Omega))$ for weak energy solutions. If we can put on a condition on $u$ or any of the data to ensure that $u \in L^2(Q_T)$, we would have a condition under which weak energy solutions are unique. Hopefully, no such condition is required, but will perhaps follow from some other estimate.
\end{obs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%				APPENDICES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{appendices}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		A
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Notation and important spaces}
Throughout this note $\Omega \subset \mathbb{R}^d$ will be a bounded domain, and $\partial \Omega$ will be its boundary. Furthermore we define $Q_T = \{ (x,t): x \in \Omega, t\in [0,T] \}$, and $\Gamma_T$ is the parabolic boundary, i.e. $\Gamma_T = \{(x,t): x \in \partial \Omega, t \in [0,T]\} \bigcup \{(x,t): x \in \Omega, t=0\}$.

\subsection{Function spaces}
Most, if not all, of the notation concerning function spaces will follow the notation in \citep{evans} (see in particular Ch. 5).

To start off $C^k(U)$ is the set of all functions that are $k$ times continuously differentiable in $U \subset \mathbb{R}^n$. A norm for continuous functions is
\begin{equation*}
	||u||_{C(\bar{U})} = \underset{x\in U}{\text{sup}}|u(x)|.
\end{equation*}
Let now $0 < \gamma \leq 1$.
\begin{mydef}[Hölder continuous]
The $\gamma^{th}$-Hölder seminorm of $u: U \to \mathbb{R}$ is
	\begin{equation*}
	|u|_{C^{0,\gamma}(\bar{U}))} = \underset{\underset{x \neq y}{x,y \in U}}{\text{sup}} \left\{\frac{|u(x)-u(y)|}{|x-y|^\gamma} \right\}
	\end{equation*}
and the $\gamma^{th}$-Hölder norm is
\begin{equation*}
||u||_{C^{0,\gamma}} = ||u||_{C(\bar{U})} + |u|_{C^{0,\gamma}}.
\end{equation*}
\end{mydef}
We continue by defining the Hölder spaces:
\begin{mydef}[Hölder space]
The Hölder space $C^{k,\gamma}(\bar{U})$ consists of all functions $u \in C^k(\bar{U})$ for which the norm
\begin{equation*}
 ||u||_{C^{k,\gamma}(\bar{U})} = \sum_{|\alpha| \leq k}||D^\alpha u||_{C(\bar{U})} + \sum_{|\alpha| = k} |D^\alpha u|_{C^{0,\gamma}(\bar{U})}
\end{equation*}
is finite.
\end{mydef}
%%%%%%%%%%%%%%%%%%
%		B
%%%%%%%%%%%%%%%%%%
\section{Passing derivative inside the integral}
\label{sec:derivative}

@@

To get the more general (\ref{diff_int}), we simply apply this result for each individual spatial dimension while keeping the others fixed.
%%%%%%%%%%%%%%%%%%%
%		C
%%%%%%%%%%%%%%%%%%%
\section{Some major theorems}
We now consider the problem of determining a function $u = u(x,t)$ in $\overline{Q}_T$ so that
\begin{equation}
\label{lady_parabolic_eq}
	u_t - \sum_{i=1}^d\frac{d}{dx_i}a_i(x,t,u,\nabla u) + a(x,t,u,\nabla u) = 0
\end{equation}
in $Q_T$ and on $\Gamma_T$
\begin{equation}
\label{lady_bc}
	u\big|_{\Gamma_T} = \psi\big|_{\Gamma_T}
\end{equation}
for some known function $\psi$.

@@

	\item For $(x,t) \in \overline{Q}_T$, $|u| \leq M$ and arbitrary $p$ the functions $a_i(x,t,u,p)$ and $a(x,t,u,p)$ are continuous, the $a_i(x,t,u,p)$ are differentiable with respect to $x$, $u$ and $p$ and the following inequalities are satisfied
	\begin{equation}
	\label{exist_cond3}
		\begin{cases}
			\nu\xi^2 \leq \sum_{i,j=1}^d\frac{\partial a_i(x,t,u,p)}{\partial p_j}\xi_i \xi_j \leq \mu \xi^2 \\
			\sum_{i=1}^d \left(|a_i| + |\frac{\partial a_i}{\partial u}|\right)(1+|p|) + \sum_{i,j=1}^d |\frac{\partial a_i}{\partial x_j}| + |a| \leq \mu (1 + |p|)^2. 		
		\end{cases}
	\end{equation}
	where $\nu$ and $\mu$ are positive numbers.

	\item For $(x,t) \in \overline{Q}_T$, $|u| \leq M$ and $|p| \leq M_1$, the functions $a_i$, $a$, $\frac{\partial a_i}{\partial p_j}$, $\frac{\partial a_i}{\partial u}$, and $\frac{\partial a_i}{\partial x_i}$ are continuous functions satisfying a Hölder condition in $x$, $t$, $u$ and $p$ with exponents $\beta$, $\frac{\beta}{2}$, $\beta$ and $\beta$ respectively.

@@

\subsection{This existence result applied to the GPME}
The general porous medium equation we are concerned with can be written
\begin{equation*}
u_t - \nabla \cdot (\nabla \Phi(u) ) - f(x,t) = 0,
\end{equation*}
which is of the form (\ref{lady_parabolic_eq}) with
\begin{equation}
a_i(x,t,u,\nabla u) = \Phi'(u) u_{x_i}, \quad a(x,t,u,\nabla u) = -f(x,t).
\end{equation}

@@

	In the general porous medium equation
	\begin{equation*}
		A(x,t,u,p) = -f(x,t) - \sum_{i=1}^d \Phi''(u)p_i,
	\end{equation*}
	which means $A(x,t,u,0) = -f(x,t)$ (Also see that we need $\Phi \in C^2(\mathbb{R})$). Thus, according to (\ref{exist_cond1}) we need constants $b_1$ and $b_2$ so that
	\begin{equation*}
		f(x,t)u \leq b_1 u^2 + b_2.
	\end{equation*}
	We are able to choose $b_1$ and $b_2$ if, for example, $f(x,t)$ is bounded in $\overline{Q}_T$.

	\item We need $a_i(x,t,u,p)$ and $a(x,t,u,p)$ to continuous. This translates to requiring that $\Phi'(u)$ and $f(x,t)$ are continuous. In addition $a_i(x,t,u,p)$ needs to be differentiable with respect to $x$, $t$, $u$ and $p$, which in our case means that $\Phi''(u)$ needs to be continuous.

	Considering the first inequality in (\ref{exist_cond3}) we have
	\begin{equation*}
		\sum_{i,j=1}^d \frac{\partial a_i(x,t,u,p)}{\partial p_j} \xi_i \xi_j = \sum_{i=1}^d \Phi'(u)\xi_i^2 =\Phi'(u)\xi^2.
	\end{equation*}
	Assuming that $\Phi'(u)$ is strictly positive and continuous for $|u|\leq M$ we can set
	\begin{equation}
	0 < \nu = \text{inf}_{|u| \leq M}\Phi'(u) < \text{sup}_{|u| \leq M}\Phi'(u) \leq \mu.
	\end{equation}

	After establishing that
	\begin{equation*}
		\begin{cases}
			a_i(x,t,u,p) &= \Phi'(u)p_i \\
			\frac{\partial a_i(x,t,u,p)}{\partial u} &= \Phi''(u)p_i \\
			\frac{\partial a_i(x,t,u,p)}{\partial x_j} &= 0,
		\end{cases}	
	\end{equation*}
	we put it into the left hand side of the second inequality of (\ref{exist_cond3}) as
	\begin{align*}
	&\sum_{i=1}^d\left( |a_i| + \left| \frac{\partial a_i}{\partial u}\right| \right)(1+|p|) + \sum_{i,j}^d\left| \frac{\partial a_i}{\partial x_j} \right| + |a| \\
	&= \sum_{i=1}^d\left( |\Phi'(u)| + |\Phi''(u)| \right)|p_i|(1+|p|) + |f(x,t)| \\
	&= (|\Phi'(u)| + |\Phi''(u)|)(1+|p|)\sum_{i=1}^d|p_i| + |f(x,t)|.
	\end{align*}
	By the equivalence of $l_p$-norms in finite dimensions $\sum_i |p_i| \leq C|p|$. Furthermore, we assume $\Phi''(u)$ to be continuous for $|u|\leq M$, then
	\begin{equation*}
	(|\Phi'(u)| + |\Phi''(u)|)(1+|p|)\sum_{i=1}^d|p_i| + |f(x,t)| \leq K(|p| + |p|^2) + |f(x,t)|,
	\end{equation*}
	where $K = C\cdot \text{sup}_{|u|\leq M}(|\Phi'(u)| + |\Phi''(u)|)$. Now we are almost done. All that remains is noticing that
	\begin{align*}
	K(|p| + |p|^2) + |f(x,t)| &\leq K(|p| + |p|^2) + ||f||_{\infty}(1+|p|) \\
	&\leq \text{max}\{ K, ||f||_\infty \} (1+|p|)^2.
	\end{align*}
	So we can set $\mu = \text{max}\{K, ||f||_\infty, \text{sup}_{|u|\leq M}\Phi'(u) \}$, and both inequalities in (\ref{exist_cond3}) are satisfied.

	\item To reiterate, we need the functions
	\begin{equation*}
		\begin{cases}
			a_i(x,t,u,p) &= \Phi'(u)p_i \\
			a(x,t,u,p) &= -f(x,t) \\
			\frac{\partial a_i(x,t,u,p)}{\partial p_j} &= \delta_{ij}\Phi'(u) \\
			\frac{\partial a_i(x,t,u,p)}{\partial u} &= \Phi''(u)p_i \\
			\frac{\partial a_i(x,t,u,p)}{\partial x_j} &= 0
		\end{cases}
	\end{equation*}
	to be Hölder continuous in $x$, $t$, $u$ and $p$ with exponents $\beta$, $\frac{\beta}{2}$, $\beta$ and $\beta$ respectively. If we choose $\beta = 1$ (i.e. Lipschitz continuous for all variables except $t$) the only additional assumption we need to make on $\Phi$ is that $\Phi^{(3)}(u)$ is bounded for $|u| \leq M$. The additional assumptions we need to make on $f$ is that it needs to be Lipschitz continuous with respect to $x$ and that
	\begin{equation*}
	|f(x,t) - f(x,s)| \leq C|t-s|^\frac{1}{2}
	\end{equation*}
	for some constant $C$.

\end{enumerate}
\end{appendices}
